\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-26 paper/experiments.tex
paper: removed experiments for queries 5 and 10

Queries 1-5 are on the CDC data. In Query~\ref{q1}, we calculate the average height for
users based on their income data. In Query~\ref{q2}, we compare cholesterol levels for
individuals with low, medium, and high incomes spectrum and above a certain weight. In
Query~\ref{q3}, we extract the maximum blood lead levels for children under the age of 6
years. In Query~\ref{q4}, we calculate the average systolic blood pressure, by gender, for
subjects with a body mass index indicating obesity. In Query~\ref{q5}, we extract the age,
gender, triglyceride levels, and waist circumference from individuals with high triglyceride
levels.

Queries 6-10 are on the FCC data. In Query~\ref{q6}, we calculate the average income for
survey participants, based on their bootcamp attendance. In Query~\ref{q7} estimates the
average age of women from the United States who participated. In Query~\ref{q8}, we
calculate the average amount of money survey participants with student debt destined to
learning based on their school degree. In Query~\ref{q9}, we join the FCC data with a
reference table provided by the World Bank which summarizes GDP per-capita across various
countries\cite{worldbank-data}. The query calculates the average GDP per-capita for
participants based on whether or not they attended a bootcamp. Finally, in Query~\ref{q10},
we identify individuals from countries with GDP per-capita of \$5000 or less who earn
\$100,000 or more post-bootcamp.

@@

Figure~\ref{fig:runtimes} provides a summary of the performance results. The first plot
shows average running times for \ProjectName{} plans in two configurations:
quality-optimized and runtime-optimized. The second plot shows, for comparison, the average
running times required for each query when performing imputation at the base tables.  In all
cases, running a query through \ProjectName{} is cheaper than imputing a single base table,
with performance improvement on a factor of ten.

@@

Figure~\ref{fig:plantimes} provides a summary of the planning times for each of the queries.
We exclude the planning time for queries that impute at base table, as that requires no
planning. In the median query across a variety of queries and choices of $\alpha$, planning
constituted 8.5 percent of total runtime by \ProjectName{}.

>>>>

Queries 1-4 are on the CDC data. In Query~\ref{q1}, we calculate the average height for
users based on their income data. In Query~\ref{q2}, we compare cholesterol levels for
individuals with low, medium, and high incomes spectrum and above a certain weight. In
Query~\ref{q3}, we extract the maximum blood lead levels for children under the age of 6
years. In Query~\ref{q4}, we calculate the average systolic blood pressure, by gender, for
subjects with a body mass index indicating obesity.

Queries 5-8 are on the FCC data. In Query~\ref{q6}, we calculate the average income for
survey participants, based on their bootcamp attendance. In Query~\ref{q7} estimates the
average age of women from the United States who participated. In Query~\ref{q8}, we
calculate the average amount of money survey participants with student debt destined to
learning based on their school degree. In Query~\ref{q9}, we join the FCC data with a
reference table provided by the World Bank which summarizes GDP per-capita across various
countries\cite{worldbank-data}. The query calculates the average GDP per-capita for
participants based on whether or not they attended a bootcamp.

@@

Figure~\ref{fig:runtimes} provides a summary of the performance results. The first plot
shows average running times for \ProjectName{} plans in two configurations:
quality-optimized and runtime-optimized. The second plot shows, for comparison, the average
running times required for each query when performing imputation at the base tables.  In all
cases, running a query through \ProjectName{} is cheaper than imputing a single base table,
with performance improvement on a factor of ten. This performance differential means it is feasible
to explore multiple imputations operations (including more expensive operators) when using
\ProjectName{}, in contrast to the traditional approach of base table imputation.

@@

Figure~\ref{fig:plantimes} provides a summary of the planning times for each of the queries.
We exclude the planning time for queries that impute at base table, as that requires no
planning. In the median query across a variety of queries and choices of $\alpha$, planning
constituted 8.5 percent of total runtime by \ProjectName{}. The one-standard-deviation
intervals around the mean planning time often overlap, suggesting the planning component is
constant in $\alpha$.
